Assignment 2

### 2025-03-13 code/Reddit_sentiment.qmd
adding data to hand code

reddit_posts <- read_xlsx(
  "~/repos/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# comments data
reddit_comment <- read_xlsx(
  "~/repos/repos/SURV622_Assignment/data/comments_data_clean.xlsx")

@@

```{r}
 reddit_comment_new |> count(label)
```

@@

```{r}
 reddit_posts_new |> count(label)
```

```{r}
# write posts data
writexl::write_xlsx(reddit_posts_new, "~/repos/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# write comments data
writexl::write_xlsx(reddit_comment_new, "~/repos//repos/SURV622_Assignment/data/comments_data_clean.xlsx")

@@

>>>>

reddit_posts <- read_xlsx(
  "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# comments data
reddit_comment <- read_xlsx(
  "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx")

@@

@@

Add new column for hand coding (dis)approval

```{r}
# write posts data
write_xlsx(reddit_posts_new, "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# write comments data
write_xlsx(reddit_comment_new, "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx")

@@

Separate out data for hand coding based on positive and negative scores for keyword searches rif, reduction in force, and fork in the road to concentrate comments on the topic of federal layoffs. Sample 400 comments without replacement from the negative and positive coded comments.

```{r}
sample_comments_dat <- reddit_comment |> 
  filter(search_term %in% c("rif", "reduction in force", "fork in the road"),
         label %in% c("positive", "negative")) |> 
  #sample_n(size=400) |> 
  mutate(outcome = NA)

# group members
group_members <-c("Kevin", 'Felix', "Aria", "Gloria")

sample_comments_list <- infer::rep_slice_sample(sample_comments_dat, n=100, replace = FALSE, reps=4) |> 
  group_by(replicate) |> 
  group_split()

walk(seq(1,4), function(x){

  write_xlsx(# pass data from list
    sample_comments_list[[x]] |> 
      select(-replicate), 
    # where to save, & how to name it
    str_c(
    "~/repos/SURV622_Assignment/data/comments_to_code/",
    group_members[x], ".xlsx")
  )
})

# write files to github by name
